---
title: "Find Boardgame Neighbors"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
runtime: shinyWidgets
---

```{r setup, include=FALSE}

#source("load_packages.R")
library(tidyverse)
library(recipes)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(data.table)
library(magrittr)
library(reshape2)
library(rsconnect)
library(flexdashboard)
library(flextable)
library(shiny)
library(shinyWidgets)
library(knitr)
library(DT)
library(ggridges)
source(here::here("functions/tidy_name_func.R"))
source(here::here("functions/theme_phil.R"))

```

```{r load data sources, include=F}

# laod in active files
games_dashboard  = 
        readr::read_rds(here::here("data/games_dashboard.Rdata")) %>%
        mutate(averageweight = case_when(is.na(averageweight) ~ est_averageweight,
                                         TRUE ~ averageweight)) %>%
        mutate(complexity_level = case_when(averageweight < 2 ~ 'Low (1-2)',
                                            averageweight >=2 & averageweight < 3 ~ 'Moderate (2-3)',
                                            averageweight >=3 & averageweight < 4 ~ 'High (3-4)',
                                            averageweight >=4 ~ 'Very High (4-5)')) %>%
        mutate(complexity_level = factor(complexity_level,
                                         levels = c("Low (1-2)",
                                                    "Moderate (2-3)",
                                                    "High (3-4)",
                                                    "Very High (4-5)"))) %>%
        mutate(maxplayers = case_when(maxplayers > 8 ~ 10,
                                      TRUE ~ maxplayers)) %>%
        mutate(maxplaytime = case_when(is.na(maxplaytime) ~ playingtime,
                                       TRUE ~ maxplaytime)) %>%
        mutate(maxplaytime= case_when(maxplaytime > 600 ~ 600,
                                       TRUE ~ maxplaytime)) %>%
        mutate(time_per_player = maxplayers/maxplaytime) %>%
        mutate(time_per_player = case_when(time_per_player < 1 ~ 1,
                                           TRUE ~ time_per_player)) %>%
        mutate(playingtime_level = case_when(maxplaytime < 30 ~ '<30 min',
                                             maxplaytime >= 30 & maxplaytime < 60 ~ '30-60 min',
                                             maxplaytime >=60 & maxplaytime < 120 ~ '60-120 min',
                                             maxplaytime >=120 ~ '>120 min',
                                             TRUE ~ 'Unknown')) %>%
        mutate(playingtime_level = factor(playingtime_level,
                                          levels = c('<30 min',
                                                     '30-60 min',
                                                     '60-120 min',
                                                     '>120 min',
                                                     'Unknown'))) %>%
        mutate(game = paste(name, game_id, sep = "-"))

# load game types
game_types = 
        readr::read_rds(here::here("data/game_types_filtered.Rdata")) %>%
        filter(value != 'Category: n in a row') %>%
        mutate(value = case_when(type == 'publisher' | type == 'designer' ~ gsub("\\(|\\)", "", value),
               TRUE ~ value)) %>%
        group_by(type, value) %>% 
        mutate(n_games = n_distinct(game_id)) %>%
        ungroup() %>%
        filter((type == 'designer' & n_games > 15 |
                       type != 'designer')) %>%
        filter((type == 'publisher' & n_games > 25 |
                        type != 'publisher'))

# tidy up type names
game_types_tidied = 
        game_types %>%
        mutate(value = gsub("Mechanism: ", "", gsub("Category: ", "", value)))

# load games for modeling with estimates
games_model_estimated = 
        readr::read_rds(here::here("data/games_model_estimated.Rdata")) %>%
        mutate(game = paste(name, game_id, sep = "-"))

### pca recipes and number of pcs used for distance ####
pca_recipe = readr::read_rds(here::here("models","pca_recipe.Rds"))

#pca_trained = readr::read_rds(here::here("models", "pca_trained.Rds"))


# # neighbors
# game_neighbors_cosine = 
#         readr::read_rds(here::here("data/game_neighbors_cosine.Rdata")) %>%
#         mutate(game = paste(name, game_id, sep = "-")) %>%
#         mutate(neighbor = paste(neighbor_name, neighbor_id, sep = "-"))

# get pca
# games_pca = game_neighbors_cosine %>%
#         select(neighbor_name, neighbor_id, PC1, PC2, PC3, PC4, PC5) %>%
#         unique() %>%
#         rename(name = neighbor_name,
#                game_id = neighbor_id) %>%
#         mutate(game = paste(name, game_id, sep="-"))


```


```{r now create selections}

# name of games
games = games_dashboard %>%
        pull(game) %>%
        sort()

# select number of pcs
number_pcs = paste("PC", seq(1, 50, by =1), sep="")

```

```{r tile plot function}

tile_plot = function(neighbors_cosine,
                     input_pcs=50) {
        
        # create vector
        number_pcs = paste("PC", seq(1, input_pcs), sep="")
        
        # make initial plot
        dat =  neighbors_cosine %>%
                #       arrange(desc(score)) %>%
                mutate(neighbor_name = abbreviate(neighbor_name, 60)) %>%
                group_by(neighbor_name) %>% mutate(count = n()) %>%
                ungroup() %>%
                mutate(neighbor_name = case_when(count > 1 ~ paste(neighbor_name, neighbor_yearpublished, sep="_"),
                                                 TRUE ~ neighbor_name))
        
        #return(dat)
        dat %>%
                select(neighbor_id, neighbor_name,
                       all_of(number_pcs)) %>%
                gather("component", "value",
                       -neighbor_id, -neighbor_name) %>%
                mutate(neighbor_name = factor(neighbor_name,
                                              levels = rev(dat %>% select(neighbor_name) %>% pull()))) %>%
                mutate(component = factor(component,
                                          levels = number_pcs)) %>%
                ggplot(., aes(y=neighbor_name,
                              #   color = highlight,
                              label = round(value, 2),
                              fill = value,
                              x=component))+
                geom_tile()+
                geom_text(color = 'white', size=2)+
                # scale_fill_viridis(limits = c(-8, 8),
                #                    oob = scales::squish)+
                # scale_fill_viridis(option = "A",
                #                    limits = c(-8,8),
                #                    oob = scales::squish)+
                scale_fill_gradient2(low = "orange",
                                     mid = "grey80",
                                     high = "navy",
                                     limits = c(-6, 6),
                                     oob = scales::squish)+
                # scale_fill_viridis(option = "B",
                #                    scale = )+
                theme_phil()+
                theme(legend.title = element_text()) +
                guides(fill = guide_colorbar(barwidth=10,
                                             barheight=0.5,
                                             title = "Component Score",
                                             title.position = 'top'),
                       color = "none")+
                scale_color_manual(values = c("white", "black"))
        
}

```


Column {.sidebar}
-----------------------------------------------------------------------

```{r make sidebar filters}

pickerInput('games',
            'Select a Game',
            choices = games,
            selected = "Gloomhaven-174430",
            multiple =F,
            options = list(`live-search`=TRUE))

```



<!-- ```{r get data for tables} -->

<!-- selected_game_neighbors = reactive({ -->

<!--         game_neighbors_cosine %>% -->
<!--                 filter(game == input$games) -->

<!-- }) -->


<!-- selected_ids = reactive({ -->

<!--          selected_game_neighbors() %>% -->
<!--                 select(game_id, neighbor_id) %>%  -->
<!--                 gather() %>% -->
<!--                 pull(value) %>%  -->
<!--                 unique() -->

<!-- }) -->

<!-- ``` -->


```{r get selected games}

selected_pca_input = reactive({
        
        pca_template
        
        # games_model_estimated %>%
        #         filter(game == input$games) %>%
        #         select(game_id, name, game)
        
        # bind_rows(games_model_estimated %>%
        #                                   filter(game == input$games),
        #                           pca_recipe$template %>%
        #                                   mutate(game = paste(name, game_id, sep="-")) %>%
        #                                   filter(game != input$games))
        # 
        
})

# # prep selected games alongside other
# selected_pca_out = reactive({
#         
#         pca_recipe %>%
#         prep(strings_as_factor = F) %>%
#         bake(new_data = bind_rows(games_model_estimated %>%
#                                           filter(game == input$games),
#                                   pca_recipe$template %>%
#                                           mutate(game = paste(name, game_id, sep="-")) %>%
#                                           filter(game != input$games))) %>%
#         set_names(., gsub("PC0", "PC", gsub("PC00", "PC", names(.))))
#         
# })
# 
# # get the matrix
# selected_dist_cosine = reactive({
#         
#         
#         # get cosine similarity between all games
#         dist_cosine_func(selected_pca_out() %>%
#                 mutate(.row = row_number()) %>%
#                 select(.row, starts_with("PC")) %>%
#                 select(.row, all_of(number_pcs)) %>%
#                 column_to_rownames(".row") %>%
#                 as.matrix()
#         )
#         
# })
# 
# # get the row of the selected game
# selected_row = reactive({
#         
#         # get row of game we want
#         selected_pca_out %>%
#                 mutate(.row = row_number()) %>%
#                 filter(game_id == params$game_id) %>%
#                 pull(.row)
#         
# })
# 
# 
# # now get the neighbors
# selected_neighbors_cosine = reactive({
#         
#         find_neighbors_max_func(dist_cosine()[game_row:(game_row+1),], 26) %>%
#                 filter(.row == game_row) %>%
#                 left_join(., pca_out %>%
#                                   mutate(.row = row_number()) %>%
#                                   select(.row, game_id, name, average, bayesaverage),
#                           by = c(".row")) %>%
#                 left_join(., pca_out %>%
#                                   mutate(.row_neighbor = row_number(),
#                                          neighbor_usersrated = usersrated,
#                                          neighbor_id = game_id,
#                                          neighbor_name = name,
#                                          neighbor_average = average,
#                                          neighbor_yearpublished = yearpublished,
#                                          neighbor_bayesaverage = bayesaverage) %>%
#                                   select(.row_neighbor,
#                                          neighbor_id, 
#                                          neighbor_name, 
#                                          neighbor_average, 
#                                          neighbor_bayesaverage, 
#                                          neighbor_usersrated,
#                                          neighbor_yearpublished,
#                                          starts_with("PC")),
#                           by = c(".row_neighbor"))
#         # %>%
#         #                 left_join(., 
#         #           pca_recipe$template %>% 
#         #                   filter(game_id != params$game_id) %>%
#         #                   select(game_id, averageweight) %>% 
#         #                   bind_rows(., game_model_estimated %>% 
#         #                                     select(game_id, averageweight)) %>%
#         #                   rename(neighbor_averageweight = averageweight,
#         #                          neighbor_id = game_id),
#         #           by = c("neighbor_id")) %>%
#         # rename(similarity = dist) %>%
#         # mutate(score = similarity*neighbor_bayesaverage)
# 
# })

```



Column {data-width=500}
-----------------------------------------------------------------------

### Most Similar Games

```{r show similar games}


renderTable({
        
        selected_pca_input()
        
})

# renderTable({
#         
#         selected_game_neighbors() %>%
#                 select(neighbor_id, neighbor_name, neighbor_average, neighbor_bayesaverage, similarity, score) %>%
#                 arrange(desc(similarity))
#                 
# })

# selected_game_neighbors() %>%
#      #   select(game_id, name, similarity, neighbor_id, neighbor_name, neighbor_average, neighbor_bayesaverage, score) %>%
#         head(26) %>%
#     #    arrange(desc(score)) %>%
#     #    filter(neighbor_id != params$game_id) %>%
#         rename(`similarity*bayesaverage` = score) %>%
#         mutate_if(is.numeric, round, 2) %>%
#         arrange(desc(similarity)) %>%
#         mutate_if(is.numeric, round,2) %>%
#         mutate(rank = row_number()-1) %>%
#         select(rank, neighbor_yearpublished, neighbor_id, neighbor_name, similarity,`similarity*bayesaverage`, neighbor_bayesaverage, neighbor_average, neighbor_averageweight, neighbor_usersrated) %>%
#         head(26) %>%
#         set_names(., gsub("Usersrated", "UserRatings", gsub("Geekrating", "GeekRating", str_to_title(gsub(" ", "", gsub("averageweight", "weight", gsub("yearpublished", "published", gsub("bayesaverage", "geek rating", gsub("neighbor_", "", names(.)))))))))) %>%
#         rename(ID = Id) %>%
#         select(Rank, everything()) %>%
#                         mutate(Link = paste("https://boardgamegeek.com/boardgame/", ID, sep="")) %>%
#         mutate(Rank = case_when(Rank == 0 ~ '--',
#                                 TRUE ~ as.character(Rank))) %>%
#         mutate_at(c("ID",
#                   "Published"),
#                   ~ as.character(.)) %>%
#         select(Rank, Published, ID, Name, Similarity, GeekRating, Average, Weight, UserRatings)
#       #   flextable(col_keys = c("Rank", "Published", "ID", "Name", "Similarity", "GeekRating", "Average", "Weight", "UserRatings")) %>%
#       #   bg(j = "GeekRating",
#       #      bg = bayesaverage_col_func) %>%
#       #   # bg(j = "Similarity*GeekRating",
#       #   #    bg = score_col_func) %>%
#       #   bg(j="Average",
#       #     bg = average_col_func) %>%
#       #   bg(j = "Weight",
#       #      bg = complexity_col_func) %>%     
#       #   bg(j = "UserRatings",
#       #      bg = usersrated_col_func) %>%   
#       #   bg(j = "Similarity",
#       #      bg = similarity_col_func) %>%
#       #   bold(j = c("Similarity"),
#       #              # "Average",
#       #              # "GeekRating",
#       #              # "Weight"),
#       #        part = "all") %>%
#       #   flextable::align(j = c("UserRatings",
#       #                          "Average",
#       #                          "GeekRating",
#       #                          "Weight"),
#       #                    align = "center",
#       #                    part = "all") %>%
#       #   merge_h(part = "header") %>%
#       #   # hline(j = c("UsersRated",
#       #   #                          "Average",
#       #   #                          "GeekRating",
#       #   #                          "Complexity"), 
#       #   #       part = "header") %>%
#       #   autofit() %>%
#       #   compose(j= 3,
#       #           value = as_paragraph(
#       #                   hyperlink_text(x = ID,
#       #                                  url = Link)
#       #           )) %>%
#       #   compose(j= 4,
#       #           value = as_paragraph(
#       #                   hyperlink_text(x = Name,
#       #                                  url = Link)
#       #           )) %>%
#       #   bg(., i = 1,
#       #      bg = 'grey80') %>%
#       #   # flextable::bold(j = c("ID", "Name"),
#       #   #                 part = "body") %>%
#       #   flextable::color(j = c("Name",
#       #                          "ID"),
#       #                    color ="skyblue4") %>%
#       #   flextable::align(j = c("Similarity",
#       # #        "Similarity*GeekRating",
#       #         "UserRatings",
#       #                          "Average",
#       #                          "GeekRating",
#       #                          "Weight"),
#       #                    align = "center",
#       #                    part = "all")

```

<!-- ### Most Similar, Highly Rated Games -->

<!-- ```{r show similar and highly rated games} -->

<!-- renderTable({ -->

<!--         selected_game_neighbors() %>% -->
<!--                 select(neighbor_id, neighbor_name, neighbor_average, neighbor_bayesaverage, similarity, score) %>% -->
<!--                 arrange(desc(score)) -->

<!-- }) -->

<!-- # selected_game_neighbors() %>% -->
<!-- #      #   select(game_id, name, similarity, neighbor_id, neighbor_name, neighbor_average, neighbor_bayesaverage, score) %>% -->
<!-- #         head(26) %>% -->
<!-- #     #    arrange(desc(score)) %>% -->
<!-- #     #    filter(neighbor_id != params$game_id) %>% -->
<!-- #         rename(`similarity*bayesaverage` = score) %>% -->
<!-- #         mutate_if(is.numeric, round, 2) %>% -->
<!-- #         arrange(desc(similarity)) %>% -->
<!-- #         mutate_if(is.numeric, round,2) %>% -->
<!-- #         mutate(rank = row_number()-1) %>% -->
<!-- #         select(rank, neighbor_yearpublished, neighbor_id, neighbor_name, similarity,`similarity*bayesaverage`, neighbor_bayesaverage, neighbor_average, neighbor_averageweight, neighbor_usersrated) %>% -->
<!-- #         head(26) %>% -->
<!-- #         set_names(., gsub("Usersrated", "UserRatings", gsub("Geekrating", "GeekRating", str_to_title(gsub(" ", "", gsub("averageweight", "weight", gsub("yearpublished", "published", gsub("bayesaverage", "geek rating", gsub("neighbor_", "", names(.)))))))))) %>% -->
<!-- #         rename(ID = Id) %>% -->
<!-- #         select(Rank, everything()) %>% -->
<!-- #                         mutate(Link = paste("https://boardgamegeek.com/boardgame/", ID, sep="")) %>% -->
<!-- #         mutate(Rank = case_when(Rank == 0 ~ '--', -->
<!-- #                                 TRUE ~ as.character(Rank))) %>% -->
<!-- #         mutate_at(c("ID", -->
<!-- #                   "Published"), -->
<!-- #                   ~ as.character(.)) %>% -->
<!-- #         select(Rank, Published, ID, Name, Similarity, GeekRating, Average, Weight, UserRatings) -->
<!-- #       #   flextable(col_keys = c("Rank", "Published", "ID", "Name", "Similarity", "GeekRating", "Average", "Weight", "UserRatings")) %>% -->
<!-- #       #   bg(j = "GeekRating", -->
<!-- #       #      bg = bayesaverage_col_func) %>% -->
<!-- #       #   # bg(j = "Similarity*GeekRating", -->
<!-- #       #   #    bg = score_col_func) %>% -->
<!-- #       #   bg(j="Average", -->
<!-- #       #     bg = average_col_func) %>% -->
<!-- #       #   bg(j = "Weight", -->
<!-- #       #      bg = complexity_col_func) %>%      -->
<!-- #       #   bg(j = "UserRatings", -->
<!-- #       #      bg = usersrated_col_func) %>%    -->
<!-- #       #   bg(j = "Similarity", -->
<!-- #       #      bg = similarity_col_func) %>% -->
<!-- #       #   bold(j = c("Similarity"), -->
<!-- #       #              # "Average", -->
<!-- #       #              # "GeekRating", -->
<!-- #       #              # "Weight"), -->
<!-- #       #        part = "all") %>% -->
<!-- #       #   flextable::align(j = c("UserRatings", -->
<!-- #       #                          "Average", -->
<!-- #       #                          "GeekRating", -->
<!-- #       #                          "Weight"), -->
<!-- #       #                    align = "center", -->
<!-- #       #                    part = "all") %>% -->
<!-- #       #   merge_h(part = "header") %>% -->
<!-- #       #   # hline(j = c("UsersRated", -->
<!-- #       #   #                          "Average", -->
<!-- #       #   #                          "GeekRating", -->
<!-- #       #   #                          "Complexity"),  -->
<!-- #       #   #       part = "header") %>% -->
<!-- #       #   autofit() %>% -->
<!-- #       #   compose(j= 3, -->
<!-- #       #           value = as_paragraph( -->
<!-- #       #                   hyperlink_text(x = ID, -->
<!-- #       #                                  url = Link) -->
<!-- #       #           )) %>% -->
<!-- #       #   compose(j= 4, -->
<!-- #       #           value = as_paragraph( -->
<!-- #       #                   hyperlink_text(x = Name, -->
<!-- #       #                                  url = Link) -->
<!-- #       #           )) %>% -->
<!-- #       #   bg(., i = 1, -->
<!-- #       #      bg = 'grey80') %>% -->
<!-- #       #   # flextable::bold(j = c("ID", "Name"), -->
<!-- #       #   #                 part = "body") %>% -->
<!-- #       #   flextable::color(j = c("Name", -->
<!-- #       #                          "ID"), -->
<!-- #       #                    color ="skyblue4") %>% -->
<!-- #       #   flextable::align(j = c("Similarity", -->
<!-- #       # #        "Similarity*GeekRating", -->
<!-- #       #         "UserRatings", -->
<!-- #       #                          "Average", -->
<!-- #       #                          "GeekRating", -->
<!-- #       #                          "Weight"), -->
<!-- #       #                    align = "center", -->
<!-- #       #                    part = "all") -->

<!-- ``` -->

### Why are these games similar?


```{r make tile plot}

# renderPlot({
#         
#         tile_plot(selected_game_neighbors() %>%
#                           head(25),
#           50)+
#                 theme(axis.text.x = element_text(angle=90))
#         
# })

```


Column {data-width=350}
-----------------------------------------------------------------------

```{r test}

```


### Complexity of Selected Games

<!-- ```{r show } -->

renderPlot({

        bind_rows(games_dashboard %>%
                          mutate(type = 'All Games'),
                  selected_games() %>%
                          mutate(type = 'Neighbors')) %>%
                ggplot(., aes(x=averageweight,
                              y=type,
                              fill = type))+
                geom_density_ridges(alpha = 0.7)+
                scale_fill_manual(values = c("grey60",
                                             "navy"))+
                theme_phil()+
                guides(fill = "none")

})

<!-- ``` -->

### Placing Games on Principal Components

```{r geek rating of selected games}

renderPlot({

        base = games_pca %>%
                ggplot(., aes(x=PC1,
                              y=PC2))+
                geom_point(alpha = 0.05,
                           color = 'grey60')+
                theme_phil()+
                geom_vline(xintercept = 0,
                           linetype = 'dotted')+
                geom_hline(yintercept = 0,
                           linetype = 'dotted')

        base +
                geom_point(data = games_pca %>%
                                   filter(game_id %in% selected_ids()),
                           alpha = 0.85,
                           color = 'navy')+
                theme_phil()+
                geom_vline(xintercept = 0,
                           linetype = 'dotted')+
                geom_hline(yintercept = 0,
                           linetype = 'dotted')

})


```
